### 2016-10-31 IEEEtran/designConcept_GP.tex
minor change in section V

Co-designed with the stakeholders from the test sites, YouPower provides a set of features that focus on the facilitation of behavior change process towards sustainable energy consumption that is implementable in the context of people's everyday life as a key to address the attitude-behavior gap \cite{Kollmuss2002,Schultz2002,Schultz2014} in people's environmental values (and attitudes) and their actual behavior in energy consumption. From this design experience, a number of design guidelines were derived and are stated in the following, which may be applicable to the development of environmental behavior change interventions beyond the particular case of CIVIS project. First, provide consumers accurate and actionable information about how to achieve the target behavior. At the test sites, people expressed the desire and need to do more for sustainable consumption, and they like the idea of receiving relevant and contextual suggestions and tips for sustainable consumption. 
Second, provide personalized means to motivate consumers to voluntarily practice and repeat the target behavior in the specific context of their everyday life. 
This means that provide personalized target behavior goals and allow users to freely practice and adapt the goals. 
This facilitates the sense of competence and autonomy which promotes and enhances motivation for behavior change. 
Third, foster consumers' intrinsic motivation to engage in the behavior change. 
People are skeptical about how much money they can save by using less energy in households but are driven by intrinsic motives as well as altruistic and environmental values. Social and community-oriented features as those designed in YouPower clearly articulate those values to foster user motivation.

>>>>

\noindent Co-designed with the stakeholders from the test sites, YouPower provides a set of features that facilitate users' behavior change process towards sustainable energy consumption that is implementable in users' daily life as a key to bridge the attitude-behavior gap of people's environmental values (and attitudes) and their actual behavior in energy consumption \cite{Kollmuss2002,Schultz2002,Schultz2014}. From this design experience, a number of design guidelines were derived and are stated in the following, which may be applicable to the development of environmental behavior change interventions beyond the particular case of CIVIS project. First, provide consumers accurate and actionable information about how to achieve the target behavior. At the test sites, people expressed the desire and need to do more for sustainable consumption, and they like the idea of receiving relevant and contextual suggestions and tips for sustainable consumption. 
Second, provide personalized means and goals to motivate consumers to voluntarily practice and repeat the target behavior in the specific context of their everyday life. 
Allow users to freely practice and adapt the process. This facilitates the sense of competence and autonomy which promotes and enhances motivation for behavior change \cite{Ryan2000}. 
Third, foster consumers' intrinsic motivation to engage in the behavior change process. 
People in the test sites are skeptical about how much money they can actually save by using less energy in households but are driven by intrinsic motives as well as altruistic and environmental values. The social and community-oriented features as those designed in YouPower articulate those values to foster user motivation.
